experiment 1

### 2021-10-26 experiments/experiment 1/experiment-1.Rmd
Moved R functions to R directory in root of project in preparation for possible structuring as package.

@@

library(microxanoxBeta)
if (packageVersion("microxanoxBeta") < package_version("0.2.3")) {
  stop("microxanox version needs to be at least 0.2.3!")
}
library(tidyverse)
library(patchwork)
library(here)
source(here("experiments/r functions/various_useful_functions.r"))
zero <- 0 ## don't change
unity <- 1 ## don't change!!!
options(mc.cores = 8)
eval_dynamics_flag <- TRUE
```

@@

```{r}
options(mc.cores = 7)
```

>>>>

```{r setup}

@@

library(microxanoxBeta)
if (packageVersion("microxanoxBeta") < package_version("0.2.3")) {
  stop("microxanox version needs to be at least 0.2.3!")
}
library(tidyverse)
library(patchwork)
library(here)
source(here("R/various_useful_functions.r"))
zero <- 0 ## don't change
unity <- 1 ## don't change!!!
options(mc.cores = 8)
eval_dynamics_flag <- TRUE
```

@@

```{r}
options(mc.cores = 8)
```
